%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A clean template for an academic CV. This is a short summary version.
%
% Uses tabularx to create two column entries (date and job/edu/citation).
% Defines commands to make adding entries simpler.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt,a4paper]{article}

% Useful aliases
\newcommand{\UERJ}{Universidade do Estado do Rio de Janeiro}
\newcommand{\UHM}{University of Hawai`i at M\={a}noa}
\newcommand{\SOEST}{School of Ocean and Earth Science and Technology}
\newcommand{\UHEARTH}{Department of Earth Sciences}
\newcommand{\LIVEARTH}{Department of Earth, Ocean and Ecological Sciences}
\newcommand{\LIVENV}{School of Environmental Sciences}
\newcommand{\LIV}{University of Liverpool}
\newcommand{\USP}{Universidade de São Paulo}

% Identifying information
\newcommand{\Title}{Curriculum Vit\ae\ Summary}
\newcommand{\FirstName}{Leonardo}
\newcommand{\LastName}{Uieda}
\newcommand{\Initials}{L}
\newcommand{\MyName}{Prof. \FirstName\ \LastName}
\newcommand{\Me}{\underline{\LastName, \Initials}}  % For citations
\newcommand{\Email}{uieda@usp.br}
\newcommand{\PersonalWebsite}{www.leouieda.com}
\newcommand{\LabWebsite}{www.compgeolab.org}
\newcommand{\ORCID}{0000-0001-6123-9515}
\newcommand{\GitHubProfile}{leouieda}

% Names for citing coauthors
\newcommand{\Val}{Barbosa, VCF}
\newcommand{\Bi}{Oliveira Jr, VC}
\newcommand{\Paul}{Wessel, P}
\newcommand{\Joaquim}{Luis, J}
\newcommand{\Remko}{Scharroo, R}
\newcommand{\Florian}{Wobbe, F}
\newcommand{\Walter}{Smith, WHF}
\newcommand{\Dongdong}{Tian, D}
\newcommand{\Bridget}{Smith-Konter, B}
\newcommand{\Eric}{Xu, X}
\newcommand{\David}{Sandwell, DT}
\newcommand{\Carla}{Braitenberg, C}
\newcommand{\Naomi}{Ussami, N}
\newcommand{\Manoel}{D'Agrella-Filho, MS}
\newcommand{\JB}{Silva, JBC}
\newcommand{\Dai}{Sales, DP}
\newcommand{\Figura}{Melo, FF}
\newcommand{\Dio}{Carlos, DU}
\newcommand{\BragaVale}{Braga, MA}
\newcommand{\YLi}{Li, Y}
\newcommand{\Angeli}{Angeli, G}
\newcommand{\Peres}{Peres, G}
\newcommand{\Everton}{Bomfim, EP}
\newcommand{\Eder}{Molina, E}
\newcommand{\Gomes}{Gomes, AAS}
\newcommand{\Santiago}{Soler, SR}
\newcommand{\Agustina}{Pesce, A}
\newcommand{\Gimenez}{Gimenez, ME}
\newcommand{\Kristoffer}{Hallam, KAT}
\newcommand{\Guangdong}{Zhao, G}
\newcommand{\Bo}{Chen, B}
\newcommand{\JLiu}{Liu, J}
\newcommand{\LChen}{Chen, L}
\newcommand{\RGuo}{Guo, R}
\newcommand{\MKaban}{Kaban, MK}
\newcommand{\Lindsey}{Heagy, LJ}
\newcommand{\Lion}{Krischer, L}
\newcommand{\Rene}{Gassmoeller, R}
\newcommand{\Bane}{Sullivan, CB}
\newcommand{\Jens}{Klump, JF}
\newcommand{\LBarba}{Barba, LA}
\newcommand{\JBazan}{Bazan, J}
\newcommand{\JBrown}{Brown, J}
\newcommand{\RGuimera}{Guimera, RV}
\newcommand{\MGymrek}{Gymrek, M}
\newcommand{\AHanna}{Alex Hanna}
\newcommand{\KHuff}{Huff, KD}
\newcommand{\DKatz}{Katz, DS}
\newcommand{\CMadan}{Madan, CR}
\newcommand{\KMoerman}{Moerman, KM}
\newcommand{\KNiemeyer}{Niemeyer, KE}
\newcommand{\JPoulson}{Poulson, JL}
\newcommand{\PPrins}{Prins, P}
\newcommand{\KRam}{Ram, K}
\newcommand{\ARokem}{Rokem, A}
\newcommand{\Arfon}{Smith, AM}
\newcommand{\GThiruvathukal}{Thiruvathukal, GK}
\newcommand{\KThyng}{Thyng, KM}
\newcommand{\BWilson}{Wilson, BE}
\newcommand{\Yehudi}{Yehudi, Y}
\newcommand{\Remi}{Rampin, R}
\newcommand{\Hugo}{van Kemenade, H}
\newcommand{\MattTurk}{Turk, M}
\newcommand{\Shapero}{Shapero, D}
\newcommand{\Anderson}{Banihirwe, A}
\newcommand{\Leeman}{Leeman, J}
\newcommand{\JEbbing}{Ebbing, J}
\newcommand{\AGuy}{Guy, A}
\newcommand{\JFarquharson}{Farquharson, J}
\newcommand{\AKushnir}{Kushnir, A}
\newcommand{\FWadsworth}{Wadsworth, F}
\newcommand{\LPerozzi}{Perozzi, L}
\newcommand{\MWieczorek}{Wieczorek, MA}
\newcommand{\LLi}{Li, L}
\newcommand{\Ricardo}{Trindade, RIF}
\newcommand{\Gelson}{Souza Junior, GF}
\newcommand{\Janine}{Carmo, J}
\newcommand{\Roger}{Fu, R}

% Load packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Full Unicode support for non-ASCII characters
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[TU]{fontenc}

% Set main fonts
\usepackage[sfdefault]{atkinson}
\usepackage[ttdefault]{sourcecodepro}

% Icon fonts
\usepackage{fontawesome5}
\usepackage{academicons}

% Disable hyphenation
\usepackage[none]{hyphenat}

% Control the font size
\usepackage{anyfontsize}

% For fancy and multipage tables
\usepackage{tabularx}
\usepackage{ltablex}

% For new environments
\usepackage{environ}

% Manage dates and times
\usepackage{datetime}

% Set the page margins
\usepackage{geometry}

% To get the total page numbers (\pageref{LastPage})
\usepackage{lastpage}

% Control spacing in enumerates
\usepackage{enumitem}

% Use custom colors
\usepackage[usenames,dvipsnames]{xcolor}

% Configure section titles
\usepackage{titlesec}

% Fancy header configuration
\usepackage{fancyhdr}

% Control PDF metadata and links
\usepackage[colorlinks=true]{hyperref}


% Template configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\geometry{%
  margin=12.5mm,
  headsep=0mm,
  headheight=0mm,
  footskip=5mm,
  includehead=true,
  includefoot=true
}

% Custom colors
\definecolor{mediumgray}{gray}{0.5}
\definecolor{lightgray}{gray}{0.9}
\definecolor{mediumblue}{HTML}{2060c2}
\definecolor{lightblue}{HTML}{a0c3ff}

% No indentation
\setlength\parindent{0cm}

% Increase the line spacing
\renewcommand{\baselinestretch}{1.1}
% and the spacing between rows in tables
\renewcommand{\arraystretch}{1.25}

% Remove space between items in itemize and enumerate
\setlist{nosep}

% Set the spacing and format of sections
\titleformat{\section}
  {\normalfont\Large\mdseries} % format
  {} % label
  {0pt} % separation (left separation for hang)
  {} % text before title
  [\titlerule] % text after title
\titlespacing*{\section}
  {0pt} % left pad
  {0.1cm} % before
  {0cm} % after

% Disable number of sections. Use this instead of "section*" so that the sections still
% appear as PDF bookmarks. Otherwise, would have to add the table of contents entries
% manually.
\makeatletter
\renewcommand{\@seccntformat}[1]{}
\makeatother

% Define a new environment to place all CV entries in a 2-column table.
% Left column are the dates, right column the entries.
\newcommand{\TablePad}{\vspace{-0.2cm}}
\NewEnviron{EntriesTableDuration}{
\TablePad
\begin{tabularx}{\textwidth}{@{}p{0.10\textwidth}@{\hspace{0.02\textwidth}}p{0.88\textwidth}@{}}
  \BODY
\end{tabularx}
\TablePad
}
\NewEnviron{EntriesTableYear}{
\TablePad
\begin{tabularx}{\textwidth}{@{}p{0.05\textwidth}@{\hspace{0.01\textwidth}}p{0.94\textwidth}@{}}
  \BODY
\end{tabularx}
\TablePad
}

% Macros to set the year and duration on the left column
\newcommand{\Duration}[2]{\fontsize{10pt}{0}\selectfont \texttt{#1-#2}}
\newcommand{\Year}[1]{\fontsize{10pt}{0}\selectfont \texttt{#1}}
\newcommand{\Ongoing}{on}
\newcommand{\Future}{future}

% Macros to add links and mark publications
\newcommand{\DOI}[1]{DOI: \href{https://doi.org/#1}{#1}}
\newcommand{\Website}[1]{\href{https://#1}{#1}}
\newcommand{\Preprint}[1]{Preprint: \href{https://doi.org/#1}{#1}}
\newcommand{\GitHub}[1]{GitHub: \href{https://github.com/#1}{#1}}

% Define command to insert month name and year as date
\newdateformat{monthyear}{\monthname[\THEMONTH], \THEYEAR}

% Configure a fancy footer
\newcommand{\Separator}{\hspace{3pt}|\hspace{3pt}}
\newcommand{\FooterFont}{\footnotesize\color{mediumgray}}
\pagestyle{fancy}
\fancyhf{}
\lfoot{%
  \FooterFont{}
  \MyName{}
  \Separator{}
  \Title{}
}
\rfoot{%
  \FooterFont{}
  Last updated: \monthyear\today{}
  \Separator{}
  \thepage\space of\space \pageref*{LastPage}
}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{1pt}
\preto{\footrule}{\color{lightgray}}

% Metadata for the PDF output and control of hyperlinks
\hypersetup{
  colorlinks,
  allcolors=mediumblue,
  breaklinks=true,
  pdftitle={\Title{} - \MyName},
  pdfauthor={\MyName},
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{minipage}[t]{0.5\textwidth}
  {\fontsize{20pt}{0}\selectfont\MyName}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  \begin{flushright}
    \Title{}
  \end{flushright}
\end{minipage}
\\[-0.1cm]
\textcolor{lightgray}{\rule{\textwidth}{3pt}}
\begin{minipage}[t]{0.5\textwidth}
  ORCID: \href{https://orcid.org/\ORCID}{\ORCID}
  \\
  Research Group: \Website{\LabWebsite}
  \\
  Website: \Website{\PersonalWebsite}
  \\
  Email: \href{mailto:\Email}{\Email}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  \begin{flushright}
  Departamento de Geofísica
  \\
  Instituto de Astronomia, Geofísica e Ciências Atmosféricas
  \\
  Universidade de São Paulo
  \\
  Rua do Matão, 1226. São Paulo - SP. Brazil. 05508-090
  \end{flushright}
\end{minipage}
\vspace{0.3cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Professional Appointments}

\begin{EntriesTableDuration}
  \Duration{2023}{\Ongoing}  &
  \textbf{Professor Doutor}, \USP, Brazil
  \\
  \Duration{2019}{2023}  &
  \textbf{Lecturer}, \LIV, UK
  \\
  \Duration{2017}{2019}  &
  \textbf{Visiting Researcher}, \UHM, USA
  \\
  \Duration{2014}{2018}  &
  \textbf{Professor Assistente}, \UERJ, Brazil
\end{EntriesTableDuration}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Community Service}

\begin{EntriesTableDuration}
  \Duration{2022}{\Ongoing} & \textbf{Board Member}, Software Underground, \Website{softwareunderground.org}
  \\
  \Duration{2024}{\Ongoing} & \textbf{Advisory Council Member}, EarthArXiv, \Website{eartharxiv.org}
  \\
  \Duration{2022}{2923} & \textbf{Advisory Committee Member}, pyOpenSci, \Website{www.pyopensci.org}
  \\
  \Duration{2019}{2022} & \textbf{Topic Editor}, Journal of Open Source Software, \Website{joss.theoj.org}
\end{EntriesTableDuration}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

\begin{EntriesTableDuration}
  \Duration{2011}{2016}  &
  \textbf{PhD in Geophysics}, Observatório Nacional, Brazil.
  \DOI{10.6084/m9.figshare.16883689}
  \\
  \Duration{2010}{2011}  &
  \textbf{MSc in Geophysics}, Observatório Nacional, Brazil.
  \DOI{10.6084/m9.figshare.16882300}
  \\
  \Duration{2004}{2009}  &
  \textbf{BSc in Geophysics}, Universidade de São Paulo, Brazil.
  \DOI{10.6084/m9.figshare.963547}
\end{EntriesTableDuration}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Open Research Software}

\begin{EntriesTableDuration}
  \Duration{2010}{\Ongoing} &
  \textbf{Fatiando a Terra} | \Website{www.fatiando.org}
  \newline
  \textit{Python tools for geophysical data processing, forward modeling, and inversion}
  \newline
  Role: Project founder, core developer, Steering Council Member
  \\
  \Duration{2017}{\Ongoing} &
  \textbf{PyGMT} | \Website{www.pygmt.org}
  \newline
  \textit{A Python interface for the Generic Mapping Tools}
  \newline
  Role: Project founder, developer, advisor
  \\
  \Duration{2017}{\Ongoing} &
  \textbf{The Generic Mapping Tools (GMT)} | \Website{www.generic-mapping-tools.org}
  \newline
  \textit{A data processing and mapping toolbox for the Earth, Ocean, and Planetary Science}
  \newline
  Role: Community stewardship advisor, set up the website + forum + GitHub workflow
  \\
  \Duration{2022}{\Ongoing} &
  \textbf{xlandsat} | \Website{compgeolab.org/xlandsat}
  \newline
  \textit{Load Landsat remote sensing scenes in Python and xarray}
  \newline
  Role: Creator and sole developer
  \\
  \Duration{2009}{2016} &
  \textbf{Tesseroids} | \Website{tesseroids.leouieda.com}
  \newline
  \textit{Forward modeling of gravitational fields in spherical coordinates}
  \newline
  Role: Creator and sole developer
\end{EntriesTableDuration}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Open Educational Resources}

\begin{EntriesTableYear}
  \Year{2022} &
  \textbf{A Quick Introduction to Machine Learning}.
  \GitHub{leouieda/ml-intro}.
  \\
  \Year{2023} &
  \textbf{Remote Sensing with Python}.
  \GitHub{leouieda/remote-sensing}.
  \\
  \Year{2023} &
  \textbf{Lithosphere Dynamics with Python}.
  \GitHub{leouieda/lithosphere}.
  \\
  \Year{2022} &
  \textbf{Terrestrial Gravimetry with Python}.
  \GitHub{leouieda/gravity-processing}.
\end{EntriesTableYear}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Grants and Fellowships}

\begin{EntriesTableDuration}
  \Duration{2022}{\Ongoing}  &
  \textbf{Towards individual-grain paleomagnetism: Translating regional-scale geophysics to the nascent field of magnetic microscopy}.
  \newline
  Royal Society.
  \Me{} (PI); \Ricardo{}.
  Award: \href{https://www.compgeolab.org/news/rsoc-mag-microscopy-2022.html}{IES\textbackslash{}R3\textbackslash{}213141}
  \\
  \Duration{2020}{\Ongoing}  &
  \textbf{A Sustainable Plan for the Future of the Generic Mapping Tools}.
  \newline
  NSF-EAR.
  \Paul{} (PI); \Me{}.
  Award: \href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=1948602}{1948602}.
  \\
  \Duration{2020}{2023}  &
  \textbf{SSI Fellowship Programme}.
  \newline
  Software Sustainability Institute.
  \Me{} (PI).
  Award: \Website{software.ac.uk/about/fellows}
  \\
  \Duration{2018}{2024}  &
  \textbf{The EarthScope/GMT Analysis and Visualization Toolbox}.
  \newline
  NSF-EAR.
  \Paul{} (PI); \Me{}; \Bridget{}.
  Award: \href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=1829371}{1829371}.
\end{EntriesTableDuration}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Selected Invited Presentations}

\begin{EntriesTableYear}
\Year{2021}  &
  \textbf{Design useful tools that do one thing well and work together: rediscovering the UNIX philosophy while building the Fatiando a Terra project}.
  \newline
  AGU 2021.
  \Me; \LLi; \Santiago; \Agustina.
  \GitHub{fatiando/agu2021}.
  \\
  &
  \textbf{Open-science for gravimetry: tools, challenges, and opportunities}.
  \newline
  GFZ Helmholtz Centre Potsdam.
  \Me; \Santiago; \Agustina.
  \GitHub{leouieda/2021-06-22-gfz}.
  \\
\Year{2021}  &
  \textbf{Fatiando a Terra: Open-source tools for geophysics}.
  \newline
  Geophysical Society of Houston.
  \Me; \Santiago; \Agustina.
  \GitHub{fatiando/2021-gsh}.
  \\
\Year{2020}  &
  \textbf{Geophysical research powered by open-source}.
  \newline
  Christian Albrechts Universität zu Kiel.
  \Me.
  \GitHub{leouieda/2020-07-01-kiel}.
\end{EntriesTableYear}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Publication Highlights}

\begin{EntriesTableYear}
\Year{2023}  &
  \textbf{Full vector inversion of magnetic microscopy images using Euler deconvolution as a priori information}.
  \newline
  EarthArXiv.
  \DOI{10.31223/X5QD5Z}.
  \newline
  \Gelson; \Me; \Ricardo; \Janine; \Roger.
  \GitHub{compgeolab/micromag-euler-dipole}.
  \\
\Year{2021}  &
  \textbf{Gradient-boosted equivalent sources}.
  \newline
  Geophysical Journal International.
  \DOI{10.1093/gji/ggab297}.
  \Preprint{10.31223/X58G7C}.
  \newline
  \Santiago; \Me.
  \GitHub{compgeolab/eql-gradient-boosted}.
  \\
\Year{2020}  &
  \textbf{Pooch: A friend to fetch your data files}.
  \newline
  Journal of Open Source Software.
  \DOI{10.21105/joss.01943}.
  \newline
  \Me; \Santiago; \Remi; \Hugo; \MattTurk; \emph{et al}.
  \GitHub{fatiando/pooch}.
  \\
\Year{2019}  &
  \textbf{The Generic Mapping Tools, Version 6}.
  \newline
  Geochemistry, Geophysics, Geosystems.
  \DOI{10.1029/2019GC008515}.
  \newline
  \Paul; \Joaquim; \Me; \Remko; \Florian; \Walter; \Dongdong.
  \\
\Year{2019}  &
  \textbf{Gravitational field calculation in spherical coordinates using variable densities in depth}.
  \newline
  Geophysical Journal International.
  \DOI{10.1093/gji/ggz277}.
  \Preprint{10.31223/osf.io/3548g}.
  \newline
  \Santiago; \Agustina; \Gimenez; \Me.
  \GitHub{pinga-lab/tesseroid-variable-density}.
  \\
\Year{2019}  &
  \textbf{Efficient 3D large-scale forward-modeling and inversion of gravitational fields in spherical coordinates with application to lunar mascons}.
  \newline
  Journal of Geophysical Research: Solid Earth.
  \DOI{10.1029/2019JB017691}.
  \Preprint{10.31223/osf.io/dzf9j}.
  \newline
  \Guangdong; \Bo; \Me; \JLiu; \MKaban; \LChen; \RGuo.
  \\
\Year{2018}  &
  \textbf{Verde: Processing and gridding spatial data using Green's functions}.
  \newline
  Journal of Open Source Software.
  \DOI{10.21105/joss.00957}.
  \newline
  \Me.
  \GitHub{fatiando/verde}.
  \\
\Year{2017}  &
  \textbf{Fast non-linear gravity inversion in spherical coordinates with application to the South American Moho}.
  \newline
  Geophysical Journal International.
  \DOI{10.1093/gji/ggw390}.
  \Preprint{10.31223/osf.io/9ba4m}.
  \newline
  \Me; \Val.
  \GitHub{pinga-lab/paper-moho-inversion-tesseroids}.
  \\
\Year{2016}  &
  \textbf{Tesseroids: forward modeling gravitational fields in spherical coordinates}.
  \newline
  Geophysics.
  \DOI{10.1190/geo2015-0204.1}.
  \newline
  \Me; \Val; \Carla.
  \GitHub{pinga-lab/paper-tesseroids}.
\end{EntriesTableYear}

\end{document}
