\documentclass[margin,line]{resume}
\usepackage[brazilian]{babel}
\usepackage[ansinew]{inputenc}
\usepackage[T1]{fontenc}

\begin{document}
\name{{\Large Leonardo Uieda}\newline
\textit{\normalsize Curriculum Vitae}}
\begin{resume}

%_______________________________________________________________________________
% Contact Information
\section{\mysidestyle Contact}\vspace{2mm}
\begin{tabular}{@{} l @{\hspace{38mm}} r}
Website:   &   www.fatiando.org/people/uieda\\
E-mail:     &   leouieda@gmail.com\\
Phone:      &   +55 21 8363 6761\\
Address:    &   Rua General Jose Cristino, 77\\
	    &   20921-400, Rio de Janeiro, RJ, Brazil
\end{tabular}

%_______________________________________________________________________________
% Research Interests
\section{\mysidestyle Research\\Interests}
Geophysical inverse problems;\\
Potential fields;\\
Open-source scientific software development;

%_______________________________________________________________________________
% Education
\section{\mysidestyle Education}
\begin{list1}
\item[] \textit{PhD in Geophysics}, 2011--Present\\
    Observatório Nacional, Rio de Janeiro, Brazil\\
    Dissertation topic:
	\textit{3D inversion of gravitational fields in spherical coordinates.
	}\\
    Advisor: \textit{Dr. Valéria C. F. Barbosa}\\
    Expected graduation date: \textit{Oct, 2015}
\vspace{2mm}
\item[] \textit{MSc in Geophysics}, 2010--2011\\
    Observatório Nacional, Rio de Janeiro, Brazil\\
    Dissertation topic:
	\textit{3D inversion of gravity gradient data by planting density
	anomalies.}\\
    Advisor: \textit{Dr. Valéria C. F. Barbosa}
\vspace{2mm}
\item[] \textit{International Exchange}, September, 2008--June, 2009\\
    York University, Toronto, Ontario, Canada
\vspace{2mm}
\item[] \textit{BSc in Geophysics}, 2004--2009\\
    Universidade de São Paulo, São Paulo, Brazil\\
    Dissertation topic:
	\textit{Usage of tesseroids in the modeling of gravity gradiometry
	data.}\\
    Advisor: \textit{Dr. Naomi Ussami}
\vspace{2mm}
\end{list1}

%_______________________________________________________________________________
% Software
\section{\mysidestyle Free software\\I develop}
\begin{list1}
\item[] Name: \textit{Tesseroids v1.1}\\
	Description:
	    \textit{Forward modeling of gravitational fields in spherical
	    coordinates using tesseroids.}\\
	Website: http://fatiando.org/software/tesseroids \\
	License: \textit{BSD License}
\vspace{2mm}
\item[] Name: \textit{Fatiando a Terra v0.0.1}\\
	Description:
	    \textit{An open source toolkit for geophysical modeling and
	    inversion.}\\
	Website: http://fatiando.org/software/fatiando \\
	License: \textit{BSD License}
\end{list1}


%_______________________________________________________________________________
% Honours and Awards
%\section{\mysidestyle Honours and\\Awards}


%_______________________________________________________________________________
% Publications
\section{\mysidestyle Selected\\Publications}
\begin{list1}
\item[] Uieda, L., and V. C. F. Barbosa (2012), Robust 3D gravity gradient
    inversion by planting anomalous densities, {\it Geophysics}, 77(4),
    G55--G66, doi:10.1190/geo2011-0388.1
\vspace{2mm}
\item[] Uieda, L., and V. C. F. Barbosa (2012), Use of the
    ``shape-of-anomaly'' data misfit in 3D inversion by planting anomalous
    densities, {\it SEG Expanded Abstracts}.
\vspace{2mm}
\item[] Carlos, D. U., L. Uieda, V. C. F. Barbosa, M. A. Braga, and A. A. S.
    Gomes (2011), In-depth imaging of an iron orebody from Quadrilatero
    Ferrifero using 3D gravity gradient inversion, {\it SEG Expanded Abstracts},
    30, 902--906, doi:10.1190/1.3628219
\vspace{2mm}
\item[] Uieda, L., E. P. Bomfim, C. Braitenberg, and E. Molina (2011), Optimal
    forward calculation method of the Marussi tensor due to a geologic
    structure at GOCE height, {\it Proc. of ``4th International GOCE User
    Workshop.''}
\end{list1}


%_______________________________________________________________________________
% Professional Experience
%\section{\mysidestyle Professional\\Experience}


%_______________________________________________________________________________
% Language Skills
\section{\mysidestyle Languages\\I speak}
\begin{list1}
  \item[] Fluent Portuguese (native)
  \item[] Fluent English - IBT TOEFL 115/120 (received 10/2007)
  \item[] Basic Spanish
\end{list1}

\end{resume}
\end{document}
