
%________________________________________________________________________________________
% @brief    LaTeX2e Resume for Kamil K Wojcicki
% @author   Kamil K Wojcicki
% @url      http://linux.dsplabs.com.au/?p=54
% @date     Decemebr 2007
% @info     Based on Latex Resume Template by Chris Paciorek 
%           http://www.biostat.harvard.edu/~paciorek/


%________________________________________________________________________________________
\documentclass[margin,line]{resume}
\begin{document}
\name{\Large Kamil K W\'ojcicki}
\begin{resume}


    %____________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}\vspace{2mm}

    \begin{tabular}{@{} l @{\hspace{38mm}} r}
    Signal Processing Laboratory                 & +61 4 1215 1771            \\
    Griffith School of Engineering               & k.wojcicki@griffith.edu.au \\
    Griffith University, Nathan Q4111, Australia & http://kamil.dsplabs.com.au\\
    \end{tabular}


    %____________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Research\\Interests}

    Speech perception, speech processing, speech enhancement, speech recognition, \\
    speaker identification and verification, statistical learning


    %____________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    {\bf Griffith University}, Brisbane, Australia \vspace{2mm}%
    \begin{list1}
    \item[] Ph.D. Research Scholar
    \begin{list2}
        \vspace*{1mm}
        \item Dissertation topic: {\sl Role of STFT Phase Spectrum in Speech Processing}
        \item Expected graduation date: February 2009
        \item Advisors:  Prof. Kuldip K. Paliwal and Dr. Stephen So
    \end{list2}
    \vspace*{2mm}
    \item[] BEng (Hons), BInfTech, April 2005
    \end{list1}


    %____________________________________________________________________________________
    % Honours and Awards
    \section{\mysidestyle Honours and\\Awards} 

    Australian Research Council (ARC) Postgraduate Research Scholarship, Brisbane, 2005-2008 \\
    Scholarship for Outstanding Academic Achievement, Griffith University, Brisbane, 2000 \\
    National Mathematics Summer School, The Australian National University, Canberra, 2000, 1999 \\
    Certificate of Excellence for Outstanding Academic Achievement, University of Tasmania, 1999 \\
    Award for Best Design, Electronics Competition, The Electronics Educators Association, 1998 


    %____________________________________________________________________________________
    % Publications
    \section{\mysidestyle Publications}

    W\'ojcicki, K.K., So, S. and K.K. Paliwal. 
    The effect of the additivity assumption on time and frequency domain {Wiener} filtering for speech enhancement.
    In {\sl Proceedings of the 8th European Conference on Speech Communication and Technology (INTERSPEECH'07)}, 
    Antwerp, Belgium, August 2007. %To appear. 

    W\'ojcicki, K.K. and K.K. Paliwal. 
    Importance of the dynamic range of an analysis window function for phase-only and magnitude-only reconstruction of speech.
    In {\sl Proceedings of the 32nd International Conference on Acoustics, Speech, and Signal Processing (ICASSP'07)},
    Honolulu, Hawaii, USA, Vol. IV, pp. 729-733, April 2007. 

    W\'ojcicki, K.K., Shannon, B.J. and K.K. Paliwal.
    Spectral subtraction with variance reduced noise spectrum estimates.
    In {\sl Proceedings of the 11th Australasian International Conference on Speech Science and Technology (SST'06)},
    Auckland, New Zealand, pp. 76-81, December 2006. 


    %____________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}

    {\bf Griffith University}, Brisbane, Australia \vspace{2mm}\\\vspace{1mm}%
    {\sl Teaching Assistant} \hfill {\bf February, 2005 -- present}\\
    Undergraduate courses
    \begin{list2}
        \vspace*{1mm}
        \item Signals and Systems
        \item Digital Signal Processing
        \item Advanced Digital Signal Processing
    \end{list2}

    {\bf Hewlett Packard}, Brisbane, Australia \vspace{2mm}\\\vspace{1mm}%
    {\sl Field Services Engineer} \hfill {\bf June, 2004 -- December, 2005} \\
    Participated in various team projects including server and workstation deployments 
    for corporate clients such as AMCOR, Blake Dawson Waldron, Bank of Queensland, 
    Pindara Private Hospital, and others. Other duties included pre-deployment site 
    inspections as well as equipment audits.

    {\bf Fujitsu Australia}, Brisbane, Australia \vspace{2mm}\\\vspace{1mm}%
    {\sl Field Services Engineer} \hfill {\bf April, 2002 -- December, 2003}\\
    Performed Point-Of-Sale (POS) deployments for various corporate clients including 
    Queensland Transport, Coles, Woolworths, and Commonwealth Bank Business Centers. 


    %____________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Computer\\Skills} 

    \begin{list2}
        \item Statistical Packages:  SPSS, SHAZAM, Statistics Toolbox (Matlab)
        \item Programming: Matlab, C/C++, Qt, PBS, SQL, Java, Perl, Visual Basic, Linux shell scripting
        \item Publishing: \LaTeXe
    \end{list2}


    %____________________________________________________________________________________
    % Referees
    \section{\mysidestyle Referees} 

    {\sl Available on request.}


%________________________________________________________________________________________
\end{resume}
\end{document}

%________________________________________________________________________________________
% EOF

